---
title: "Wertpapier Prospekt-Daten"
output: html_notebook
---

```{r}
library("rvest")
library("xml2")
# Google-Suche nach: AT0000A1X2Y2 filetype:pdf site:https://www.erstegroup.com

search_result_page <- html("https://www.google.at/search?ei=Tjm1Wv-MFsTWkwXnwJLoBw&q=AT0000A1X2Y2+filetype%3Apdf+site%3Ahttps%3A%2F%2Fwww.erstegroup.com&oq=AT0000A1X2Y2+filetype%3Apdf+site%3Ahttps%3A%2F%2Fwww.erstegroup.com&gs_l=psy-ab.3...168634.188311.0.188721.34.32.1.0.0.0.105.1697.31j1.32.0....0...1c.1.64.psy-ab..1.0.0....0.DWpY5hOqPjU")
# "//div[@class=\"upost-text\"]

# XPath for Search Result with PDF
xpath = "//h3[@class='r']/a/@href"
# xpath = "//div[@class=\"rc\"]/h3/a/@href"
# xpath = "*[@id=\"rso\"]/div/div/div[1]/div/div/h3/a"

document_links <- html_nodes(search_result_page, xpath = xpath)
document_link <- html_node(search_result_page, xpath = xpath)
# document_links <- html_nodes(search_result_page, xpath = "...")

document_link_text <- html_text(document_link)
document_link_url <- html_attr(document_link, "href")
# help(html_text)

document_links
document_link_text
document_link_url
####



```


```{r}
library("rvest")
library("xml2")
library("pdftools")

#Prospectus page
base_url = "https://www.erstegroup.com"

url = "https://www.erstegroup.com/de/ueber-uns/erste-group-emissionen/prospekte/anleihen/dip12052017"
prospectus_page <- read_html(url)

#direct path for first PDF => tr are the table rows for each document -> TODO: loop through it!
xpath = "//*[@id=\"content\"]/div/section/div[2]/div[3]/div/div[2]/table/tbody/tr[3]/td[1]/a"

#node on webpage
document_link_node <- html_node(search_result_page, xpath = xpath)
document_link_node
# document_links <- html_nodes(search_result_page, xpath = "...")

#URL target and name
document_link_url <- html_attr(document_link_node, "href")
document_link_url

document_name <- html_text(document_link_node)
document_name <- paste(document_name, '.pdf', sep="")
document_name

#full URL to PDF document
url = paste(base_url, document_link_url, sep="")
url

#get prospectus PDF
download.file(url, document_name, mode = "wb", method = "curl")


```



## Download the Prospectus PDF(s)

curl command from OS
Example:
curl -get https://www.erstegroup.com/content/dam/at/eh/www_erstegroup_com/de/Erste%20Group%20Emissionen/prospekte/anleihen/debt-issuance-prog/20170512/20170704-FT-DIP1559.pdf --output test.pdf

Examples: www.ErsteGroup.com > Investor Relations > Debt Issuance Programme > <Date> > Section: Final Terms

Example Base URL for Prospectus https://www.erstegroup.com/de/ueber-uns/erste-group-emissionen/prospekte/anleihen/dip12052017

```{r}
# Download the Prospectus PDF(s)

# curl command from OS
# curl -get https://www.erstegroup.com/content/dam/at/eh/www_erstegroup_com/de/Erste%20Group%20Emissionen/prospekte/anleihen/debt-issuance-prog/20170512/20170704-FT-DIP1559.pdf --output test.pdf

# install.packages("RCurl")
library("RCurl")

url = "https://www.erstegroup.com/content/dam/at/eh/www_erstegroup_com/de/Erste%20Group%20Emissionen/prospekte/anleihen/debt-issuance-prog/20170512/20170704-FT-DIP1559.pdf"

# PDF exists
PDFexists = url.exists(url)
if ( PDFexists ) 
{
  pdf_document = getURL(url)
}

# install.packages("pdftools")
library("pdftools")

download.file(url, "WP01.pdf", mode = "wb", method = "curl")

```

## Parse Text from PDF

in R: Some info from the Web -> looks like a lot with R and pdftools library!
  https://medium.com/@CharlesBordet/how-to-extract-and-clean-data-from-pdf-files-in-r-da11964e252e

Liad suggests to go with Python instead 
-> more powerful libraries for Natural Language Processing (NLP)!
-> THE package for NLP for Python is: nltk
Recommended book on NLP: http://www.nltk.org/book/
Package on top of it (not only sourcing from PDFs, but Doc, etc.): textract http://textract.readthedocs.io/en/stable/

Similar topic solved by a German for Financial Statements @ https://simfin.com/ 
-> Liad suggests to get in contact with him!

Product to purchase in this area is Ontotext - was featured at a recent Datathon in Sofia - https://www.datasciencesociety.net/datathon/#whatis - NLP Use Case: https://www.youtube.com/watch?v=aZIA9QfB2mk (Liad may still have access to the built solution)



Conference in Vienna coming up: https://www.wearedevelopers.com 

```{r}
# parsing code goes here
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
